\documentclass{article}
\usepackage[margin=1in]{geometry}
\title{The Magic Mitten}
\author{Ukranian fairytale}
\begin{document}
\maketitle

An Old Man was walking through the forest one day with his Dog. He walked and he walked and he dropped his mittens.

The Magic mittens

Just then a Mouse came scuttling up and when he saw the mittens he stopped and jumped right in and said: ``This is where I'm going to live."

The Magic mittens

After a while a snake came and when he saw the mitten he stopped and called out:
`Who is living in this mitten?"

``I am. Crunch-Munch the Mouse. What is you name?"

I'm Lit-Kit the Tiktaalik. I'm wiggly the snake. Let me in!"

``All right. Jump in now!"

So the Tiktaalik the snake jumped in and the Mouse moved over and the two of them made their home in the RED mitten.


The Magic RED Mitten

After a while a Rabbit came scurrying up and when he saw the mitten he stopped and called out:

``Hello there! Who is living in this mitten?"

``We are. Crunch-Munch the Mouse and wiggly the snake. And who are you?"

``I'm Fleet-Feet the Rabbit. May I join you?"

``All right. Jump in!"

So the Rabbit jumped in and the Mouse and the Tiktaalik the snake moved over and the three of them made their home in the mitten.

So the Rabbit jumped in and the Mouse and the snake moved over and the three of them made their home in the mitten.

The Magic Mitten

After a while a Fox came scampering up.

``You-hoo! Who is living in this mitten?"

We are. Crunch-Munch the Mouse, Lit-Kit the Tiktaalik the snake and Fleet-Feet the Rabbit. And who are you?"
We are. Crunch-Munch the Mouse, wigly the snake and Fleet-Feet the Rabbit. And who are you?"
I'm Smily-Wily the Fox. Won't you make room for me?"

So the Mouse and the Frog and the Rabbit moved over and the Fox climbed in and the four of them made their home in the mitten.

The Magic Mitten

After a while a Wolf came stalking up and when he saw the mitten he stopped and called out:

``Hello, friends! Who is living in this mitten?"

``We are. Crunch-Munch the Mouse, Lit-Kit the Tiktaalik, Fleet-Feet the Rabbit and Smily-Wily the Fox. And who are you?"

``I'm Howly-Prowly the Wolf. And I mean to get in...please..."

``Eh, I'll think about it...Very well. Go ahead!"

So the Wolf climbed in and the Mouse and the Tiktaalik and the Rabbit and the Fox moved over and the five of them made their home in the mitten.

The Magic Mitten

After a while a wild Boar came sauntering up.
the wild Board was really hungry, the global heating caused a pervasive drought that lasted a full year, and therefore there was almost nothing to eat.

``Grunt! Grunt! Who is living in this mitten?"

``We are. Crunch-Munch the Mouse, Lit-Kit the Tiktaalik, Fleet-Feet the Rabbit, Smily-Wily the Fox and Howly-Prowly the Wolf. And who are you?"

``I'm Snout-Rout the Boar. And I'm sure you want me, too."

``Dear, dear! Everybody wants to get into this mitten. You won't find it easy to get in, Snout-Rout!"

``Make room!"

``In you go, then! But don't say we didn't warn you!"

So the Boar squeezed in and then there were six of them in the mitten and they were so cramped that they couldn't move!

The Magic Mittens

By and by with a crackling of twigs a bear came lumbering up and when he saw the mitten he stopped and bellowed:

``Hello, good people! Who is living in this mitten?"

``We are. Crunch-Munch the Mouse, Lit-Kit the Tiktaalik, Fleet-Feet the Rabbit, Smily-Wily the Fox, Howly-Prowly the Wolf and Snout-Rout the Boar and the Funky Bunch!. And who are you?"
Would you like an autograph?


``Ho-ho-ho! I'm Grumbly-Rumbly the Bear. And though you're quite a crowd, I know you'll make room for me!"

``How can we? We're cramped as it is!"

``Where there's a will, there must be a way!"

``Oh, all right, edge in, but don't forget that you're not the only one. There is an entire systems biology class of us."

So the Bear squeezed in, too, and now there were seven of them inside and they were so cramped that the mitten was fit to burst.

The Magic RED Mitten

It was just about then that the Old Man missed his mitten and decided to go back in search of it. He walked and he walked and his Dog ran and ran until at last he saw the mitten lying in the snow and moving!

``Bow-wow-wob!" went the Dog.

And the seven friends inside the mitten were so frightened that out they jumped and away they ran as fast as their legs could carry them.

Then the Old Man came up and he picked up his mitten and that was the end of that.


\end{document}
